Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-10 WRITEUP/ms.tex
consistent notation in figures

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating global quantities for MCS, we always perform a mass-weighting. Since we operate on data on a unigrid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC. We can use the defintion \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
\end{equation}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right)^2 \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n} \right)^2 \right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$.
 In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
%
Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to show the point?}\DL{This is currently shown in \Fig{vv}}, but this depends on the evolutionary stage of \flower.
%
%\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
include a large number of stellar mass already ensembled in \flower \AP{please change $M_{cl}$ to $M_{\rm gas}$ in the figure}.
\label{fig:stellarRatio16}}
\end{figure}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass
  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
 over all times analyzed here.
Note that the scalesshown on the $y$-axes are different between the top
and bottom panels, as fewer MCCs are identified at higher $n_{\rm
  cut}$.
\label{fig:dist}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
% black dot = extragalactic GMCs in quiescent environments
Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are
from \citet{Larson81a, Heyer04a, Bolatto08a}.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).
The gray dotted lines shown in the bottom panels correspond to the various external pressures for
gas in equilibrium, see Equation~\ref{eqn:v0}. \AP{$\sigma$ should be $\sigma_{\rm gas}$}
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCCs identified in the accreting phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the
mass-size relation found for regions in the Milky Way with massive \SF
reported by \citet{Kauffmann10b}. Star symbols are color-coded by
increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
%same as \Fig{larsons_single}.
Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF \AP{please change y label to $M_{\rm gas}$; note that in Fig. \ref{fig:dist} R instead of cloud size is used; we have to pick one}.
\label{fig:MR}}
%mm}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
Definition of symbols are same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
post-starburst phase.
The variation is clearly seen between the pre-starburst through post-starburst phase.
Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{please change x label to $M_{\rm gas}$; note that this plot seems a bit redundant}
\label{fig:alphaEvol}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar). Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher
density thresholds (top right panel). \AP{please change x labels of the middle panels to $M_{\rm gas}$; $\sigma$ should be $\sigma_{\rm gas}$}
\label{fig:alpha16-28}}
\end{figure*}

@@

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
\citet{Lombardi10a} in the MW.
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

We note that similarly massive molecular structures (few times 10$^7$\,\Msun) have been
reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
However, the IGM and merger and accretion histories are not properly modeled in such simulations since
they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is
reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
%%
%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
%%
%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%%
This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in
nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.

@@

The high pressure observed in \flower (see \citealt{Pallottini17a})
is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{kohandel:2019} and to higher velocity the accretion/SN-driven outflows \citep{gallerani:2018}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also be biased high due to the resolution limit.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Velocity dispersions from bulk motions and turbulent motions of \flower in accreting (top) and
quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
The velocity dispersion from turbulent motions is higher than that from bulk motions for most MCCs in the accreting phase, but
the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion.
This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales
should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM. \AP{to guide the eye, I would draw the $x=y$ line in both panels}
% either higher resolution, or properly accounting for large scale motions.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

We compare the gas velocity dispersion from bulk motions versus turbulent motions for MCCs in the accreting
and quiescent phase in \Fig{vv}. We note that \flower displays a disturbed morphology in the accreting phase
but a disk-like morphology in the quiescent phase
(see \Fig{MCC} and \Fig{MCC28}).
Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions,
whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.
{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here
have an important contribution from large-scale rotation.} Hence, the linewidths observed in \highz molecular gas structures
on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM,
and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
\caption{Density and size of MCCs in the accreting phase of \flower.
At higher $n_{\rm cut}$, MCCs are broken into smaller MCCs and
form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. \AP{$\rho \rightarrow n$; this should stay close to Fig. \ref{fig:MR}}
\label{fig:rho}}
\vspace{0.5em}
\end{figure}

@@

%==============================================================================
%                                Back matters
%==============================================================================
% ACKNOWLEDGEMENTS
%-------------------------------------
\acknowledgements

We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.
%
TKDL acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
%mm
    M-MML acknowledges partial support by the NSF through award
    AST18-15461, and hospitality from the Insitute for Theoretical
    Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.

>>>>

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating global quantities for MCS, we always perform a mass-weighting. Since we operate on data on a unigrid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC. We can use the defintion \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
\end{equation}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
include a large number of stellar mass already ensembled in \flower 
\label{fig:stellarRatio16}}
\end{figure}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass
  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
 over all times analyzed here.
Note that the scales shown on the $y$-axes are different between the top
and bottom panels, as fewer MCCs are identified at higher $n_{\rm
  cut}$.
\label{fig:dist}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
% black dot = extragalactic GMCs in quiescent environments
Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are
from \citet{Larson81a, Heyer04a, Bolatto08a}.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).
The gray dotted lines shown in the bottom panels correspond to the various external pressures for
gas in equilibrium, see Equation~\ref{eqn:v0}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCCs in the accreting phase of \flower (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. 
Star symbols are color-coded by
increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
Red line shows the mass-size relation found for regions in the Milky Way with massive \SF \citep{Kauffmann10b}. 
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), corresponding to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see \Sec{singless} and e.g., \citealt{Lombardi10a}).
%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
%same as \Fig{larsons_single}.
%Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
%relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
For interpretation of this figure, see discussion in \Sec{MR}.
\label{fig:MR}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
Definition of symbols are same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
post-starburst phase.
The variation is clearly seen between the pre-starburst through post-starburst phase.
Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
\label{fig:alphaEvol}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar). Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher
density thresholds (top right panel).
\label{fig:alpha16-28}}
\end{figure*}

@@

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
\citet{Lombardi10a} in the MW.
Further discussions on the interpretation of this is provided in \Sec{MR}.
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been
reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
However, the IGM and merger and accretion histories are not properly modeled in such simulations since
they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is
reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
%%
%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
%%
%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%%
This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in
nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.

@@

The high pressure observed in \flower (see \citealt{Pallottini17a})
is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{kohandel:2019} and higher velocity accretion/SN-driven outflows \citep{gallerani:2018}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also be biased high due to the resolution limit.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Gas velocity dispersions from bulk motions and turbulent motions of \flower in accreting (top) and
quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
The velocity dispersion from turbulent motions is higher than that from bulk motions for most MCCs in the accreting phase, but
the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion.
This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales
should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM. 
% either higher resolution, or properly accounting for large scale motions.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$.
 In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
 % 
 Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, 
as the two are connected via the Euler equation, but this depends on the evolutionary stage of \flower (\Fig{vv}).
%
%\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}.

We compare the gas velocity dispersion from bulk motions versus turbulent motions for MCCs in the accreting
and quiescent phase in \Fig{vv}. We note that \flower displays a disturbed morphology in the accreting phase
but a disk-like morphology in the quiescent phase
(see \Fig{MCC} and \Fig{MCC28}).
Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions,
whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.

We note that \citet{Behrendt16a} similarly concluded that large scale bulk motion may mimic turbulent velocity dispersion 
due to beam smearing even though the self-rotation of each individual sub-MCCs is washed out.

{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here
have an important contribution from large-scale rotation.} Hence, the linewidths observed in \highz molecular gas structures
on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM,
and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
\caption{Density and size of MCCs in the accreting phase of \flower.
At higher $n_{\rm cut}$, MCCs are broken into smaller MCCs and
form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
\AP{$\rho \rightarrow n$}
\label{fig:rho}}
\vspace{0.5em}
\end{figure}

@@

%==============================================================================
%                                Back matters
%==============================================================================
% ACKNOWLEDGEMENTS
%-------------------------------------
% \acknowledgements

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.
%
TKDL acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
%mm
    M-MML acknowledges partial support by the NSF through award
    AST18-15461, and hospitality from the Insitute for Theoretical
    Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
